A generalization of the Bradley-Terry model for draws in chess

### 2020-10-04 inst/jebo_chess_revision2.tex
more blue text

The present work details an approach to chess analysis based on
reification of entities representing proclivity to draw, and the
first-mover (or white player) advantage.  Likelihood functions for the
players' and reified entities' strengths are defined using only
specific tournament outcomes; further, the analysis uses only game
outcome, not length.  Many hypotheses of interest to the chess
community may be analysed straightforwardly.

>>>>

The present work details an approach to chess analysis based on
reification of entities representing proclivity to draw, first-mover
(or white player) advantage, and \textcolor{blue}{the additional
  playing strength conferred by previous collusive draws.  Likelihood
  functions for the players' and reified entities' strengths are
  defined using only specific tournament outcomes.}  Many hypotheses
of interest to the chess community may be analysed straightforwardly.
